---
title: "Diamond pricing"
author: "Eric Yue"
date: "2019/4/27"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(ggplot2)
library(dplyr)
library(ggthemes)
```

## Overview

This is a Shiny app to explore the diamonds dataset in **ggplot2**, and to predict the price of a diamond. 
It's an updated version of a class project for [Developing Data Products](https://www.coursera.org/learn/data-products) as part of the **Data Science Specialization** on Coursera, April, 2019.

With the shiny app, reader can choose the cut and clarity variables in the boxcheck input. The webpage of the app is https://eric-yue.shinyapps.io/test/.

All of the code is listed at https://github.com/xmyyj001/diamonds_pricing.

## About the data 

```{r diamonds_data}
data(diamonds)
head(diamonds)

```
## Diamonds price with cut
First we can see that diamonds with different cut method, will be at very much variant pricing.
```{r diamonds_cut, echo=FALSE,message=FALSE,warning=FALSE}
g1 <- ggplot(diamonds, aes(carat, price, color = cut)) +
  geom_point() +
scale_colour_solarized("red")
g1

```

## Diamonds price with clarity
Also with the clarity property of diamonds get different price.
```{r diamonds_clarity, echo=FALSE,message=FALSE,warning=FALSE}

g <- ggplot(diamonds, aes(carat, price, color = clarity)) +
  geom_point() +
scale_colour_solarized("yellow")
g

```

## Diamonds price with Linear regression

On my shiny app, there will give the choice of cut method and clarity property, and get according price.  

Below is just an example. I have filtered the data of diamonds with condition:  cut=="Good"&clarity=="SI1", showing a linear regression line.

Applying the linear regression model, when input the cut method, clarity property and carats of the diamond, the app will predict the price accordingly.

## The plot

```{r diamonds_lm, echo=FALSE,message=FALSE,warning=FALSE}

diamonds<-filter(diamonds,cut=="Good"&clarity=="SI1")

g2 <- ggplot(diamonds)+
  geom_point(aes(carat, price, color = clarity))+
  geom_smooth(aes(carat,price),method = "lm")+  
  scale_colour_solarized("yellow")
g2

```